---
title: "Hypothesis 2"
author: "Anuhya B S"
date: "2/27/2022"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**2. Authors can be classified based on years of experience or number of books published. Highly experienced authors can definitely be expected to have larger rating counts. From a publisher point of view, it would be useful to assess if publishing works of new authors (who typically have 0-3 works published) would look promising.**

The author work experience has been divided into three categories(based on log2 (author work count) distribution):\
1. Newbie : Work count of authors less than 16\
2. Average : Work count of authors between 16 and 256\
3. Experienced : Work count of authors more than 256 \

$$H_0:\mu_N=\mu_A=\mu_E$$

```{r}
master_data = read.csv('master_dataset.csv')
```

```{r}
colnames(master_data)
```

Creating data subsets:
```{r}
new_exp <- subset(master_data, author_exp == 'newbie' | author_exp == 'experienced')
new_exp
new_avg <- subset(master_data, author_exp == 'newbie' | author_exp == 'average')
new_avg
avg_exp <- subset(master_data, author_exp == 'average' | author_exp == 'experienced')
avg_exp
```

**2-tailed Z-test to compare mean rating count b/w New-comers and Average authors:**
```{r}
m = with(new_avg,tapply(rating_count, author_exp, mean))
s = with(new_avg,tapply(rating_count, author_exp, sd))
n = with(new_avg,tapply(rating_count, author_exp, length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = 2*(1-pnorm(z))
round_p = round(p,4)
data.frame(z,p,round_p)
```

**Results: The z-score = 4.762963 and p-value = 1.907705e-06.**

Since the p-vale is less than 0.05, we have sufficient evidence to reject the null hypothesis.
This means the average rating count of new comer authors is not equal to average rating counts of average work count authors.

**2-tailed Z-test to compare mean rating count b/w New-comers and Experienced authors:**

```{r}
m = with(new_exp,tapply(rating_count, author_exp, mean))
s = with(new_exp,tapply(rating_count, author_exp, sd))
n = with(new_exp,tapply(rating_count, author_exp, length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = 2*(1-pnorm(z))
round_p = round(p,4)
data.frame(z,p,round_p)
```
**Results: The z-score = 9.482697 and p-value = *0.**

Since the p-vale is less than 0.05, we have sufficient evidence to reject the null hypothesis.
This means the average rating count of new comer authors is not equal to average rating counts of experienced authors.

**2-tailed Z-test to compare mean rating count b/w Average and Experienced authors:**

```{r}
m = with(avg_exp,tapply(rating_count, author_exp, mean))
s = with(avg_exp,tapply(rating_count, author_exp, sd))
n = with(avg_exp,tapply(rating_count, author_exp, length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = 2*(pnorm(z))
round_p = round(p,4)
data.frame(z,p,round_p)
```

**Results: The z-score = -7.434607	and p-value = 1.048789e-13.**

Since the p-vale is less than 0.05, we have sufficient evidence to reject the null hypothesis.
This means the average rating count of average work count authors is not equal to average rating counts of experienced authors.

**ANOVA TEST:**

```{r}
summary(aov(master_data$rating_count~as.factor(master_data$author_exp)))
```

**Pairwise test with unequal variances:**
```{r}
p12 = t.test(master_data$rating_count[master_data$author_exp=='newbie'],master_data$rating_count[master_data$author_exp=='average'],var.equal = F)
p12
p13 = t.test(master_data$rating_count[master_data$author_exp=='newbie'],master_data$rating_count[master_data$author_exp=='experienced'],var.equal = F)
p13
p23 = t.test(master_data$rating_count[master_data$author_exp=='average'],master_data$rating_count[master_data$author_exp=='experienced'],var.equal = F)
p23
```
**Future work : Need to apply Bonferroni correction** 

# Comparing the avg rating count for male and female authors having different work counts

**Comparing average rating counts of male newbies and female newbies**
```{r}
m = with(master_data,tapply(rating_count[author_exp=='newbie'], author_sex[author_exp=='newbie'], mean))
s = with(master_data,tapply(rating_count[author_exp=='newbie'], author_sex[author_exp=='newbie'], sd))
n = with(master_data,tapply(rating_count[author_exp=='newbie'], author_sex[author_exp=='newbie'], length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = 2*(1-pnorm(z))
round_p = round(p,4)
data.frame(z,p,round_p)
```
**Results: The z-score = 1.354282	and p-value = 0.1756464.**
We do not have enough evidence to reject the null hypothesis.
The average rating count for newbie female is equal to the average rating count of newbie male

**Comparing average rating counts of male avg work count authors and female avg work count authors**
```{r}
m = with(master_data,tapply(rating_count[author_exp=='average'], author_sex[author_exp=='average'], mean))
s = with(master_data,tapply(rating_count[author_exp=='average'], author_sex[author_exp=='average'], sd))
n = with(master_data,tapply(rating_count[author_exp=='average'], author_sex[author_exp=='average'], length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = 2*(1-pnorm(z))
round_p = round(p,4)
data.frame(z,p,round_p)
```
**Results: The z-score = 1.471525	and p-value = 0.1411493.**
We do not have enough evidence to reject the null hypothesis.
The average rating count for avg work count male authors is equal to the average rating count of avg work count female authors.

**Comparing average rating counts of male experienced and female experienced**
```{r}
m = with(master_data,tapply(rating_count[author_exp=='experienced'], author_sex[author_exp=='experienced'], mean))
s = with(master_data,tapply(rating_count[author_exp=='experienced'], author_sex[author_exp=='experienced'], sd))
n = with(master_data,tapply(rating_count[author_exp=='experienced'], author_sex[author_exp=='experienced'], length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = 2*(pnorm(z))
round_p = round(p,4)
data.frame(z,p,round_p)
```
**Results: The z-score = -0.7185741		and p-value = 0.4724034.**
We do not have enough evidence to reject the null hypothesis.
The average rating count for experienced male is equal to the average rating count of experienced female.

Pairwise T-test with unequal variances:
```{r}
p12 = t.test(master_data$rating_count[master_data$author_exp=='newbie' & master_data$author_sex=='male' ], master_data$rating_count[master_data$author_exp=='newbie'  & master_data$author_sex=='female' ], var.equal = F)
p12
p13 = t.test(master_data$rating_count[master_data$author_exp=='average' & master_data$author_sex=='male' ], master_data$rating_count[master_data$author_exp=='average'  & master_data$author_sex=='female' ], var.equal = F)
p13
p23 = t.test(master_data$rating_count[master_data$author_exp=='experienced' & master_data$author_sex=='male' ], master_data$rating_count[master_data$author_exp=='experienced'  & master_data$author_sex=='female' ], var.equal = F)
p23
```

**Comparing average rating counts of male newbie and male avg work count**
```{r}
m = with(new_avg,tapply(rating_count[author_sex=='male'], author_exp[author_sex=='male'], mean))
s = with(new_avg,tapply(rating_count[author_sex=='male'], author_exp[author_sex=='male'], sd))
n = with(new_avg,tapply(rating_count[author_sex=='male'], author_exp[author_sex=='male'], length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = 2*(1-pnorm(z))
round_p = round(p,4)
data.frame(z,p,round_p)
```
**Results: The z-score = 4.395607	and p-value = 0.**
We have sufficient evidence to reject the null hypothesis.
The average rating count for newbie male authors is not equal to the average rating count of avg work count male authors.

**Comparing average rating counts of male newbie and male experienced author**

```{r}
m = with(new_exp,tapply(rating_count[author_sex=='male'], author_exp[author_sex=='male'], mean))
s = with(new_exp,tapply(rating_count[author_sex=='male'], author_exp[author_sex=='male'], sd))
n = with(new_exp,tapply(rating_count[author_sex=='male'], author_exp[author_sex=='male'], length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = 2*(1-pnorm(z))
round_p = round(p,4)
data.frame(z,p,round_p)
```
**Results: The z-score = 9.446552	and p-value = 0.**
We have sufficient evidence to reject the null hypothesis.
The average rating count for newbie male authors is not equal to the average rating count of experienced male authors.

**Comparing average rating counts of male experienced and male avg work count**

```{r}
m = with(avg_exp,tapply(rating_count[author_sex=='male'], author_exp[author_sex=='male'], mean))
s = with(avg_exp,tapply(rating_count[author_sex=='male'], author_exp[author_sex=='male'], sd))
n = with(avg_exp,tapply(rating_count[author_sex=='male'], author_exp[author_sex=='male'], length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = 2*(pnorm(z))
round_p = round(p,4)
data.frame(z,p,round_p)
```
**Results: The z-score = -7.555948	and p-value = 0.**
We have sufficient evidence to reject the null hypothesis.
The average rating count for experienced male authors is not equal to the average rating count of avg work count male authors.

ANOVA Test:
```{r}
summary(aov(master_data$rating_count[master_data$author_sex=='male']~as.factor(master_data$author_exp[master_data$author_sex=='male'])))
```

Pairwise T-test with unequal variances:
```{r}
p12 = t.test(master_data$rating_count[master_data$author_exp=='newbie' & master_data$author_sex=='male'], master_data$rating_count[master_data$author_exp=='average' & master_data$author_sex=='male'],var.equal = F)
p12
p13 = t.test(master_data$rating_count[master_data$author_exp=='newbie' & master_data$author_sex=='male'], master_data$rating_count[master_data$author_exp=='experienced' & master_data$author_sex=='male'],var.equal = F)
p13
p23 = t.test(master_data$rating_count[master_data$author_exp=='average' & master_data$author_sex=='male'], master_data$rating_count[master_data$author_exp=='experienced' & master_data$author_sex=='male'],var.equal = F)
p23
```

**Comparing average rating counts of female newbie and female avg work count**
```{r}
m = with(new_avg,tapply(rating_count[author_sex=='female'], author_exp[author_sex=='female'], mean))
s = with(new_avg,tapply(rating_count[author_sex=='female'], author_exp[author_sex=='female'], sd))
n = with(new_avg,tapply(rating_count[author_sex=='female'], author_exp[author_sex=='female'], length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = 2*(1-pnorm(z))
round_p = round(p,4)
data.frame(z,p,round_p)
```
**Results: The z-score = 3.224229	and p-value = 0.0013**
We have sufficient evidence to reject the null hypothesis.
The average rating count for newbie female authors is not equal to the average rating count of avg work count female authors.

**Comparing average rating counts of female experienced and female newbie authors**

```{r}
m = with(new_exp,tapply(rating_count[author_sex=='female'], author_exp[author_sex=='female'], mean))
s = with(new_exp,tapply(rating_count[author_sex=='female'], author_exp[author_sex=='female'], sd))
n = with(new_exp,tapply(rating_count[author_sex=='female'], author_exp[author_sex=='female'], length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = 2*(1-pnorm(z))
round_p = round(p,4)
data.frame(z,p,round_p)
```
**Results: The z-score = 3.637264	and p-value = 0.000275549**
We have sufficient evidence to reject the null hypothesis.
The average rating count for newbie female authors is not equal to the average rating count of experienced female authors.

**Comparing average rating counts of female experienced and female avg work count**

```{r}
m = with(avg_exp,tapply(rating_count[author_sex=='female'], author_exp[author_sex=='female'], mean))
s = with(avg_exp,tapply(rating_count[author_sex=='female'], author_exp[author_sex=='female'], sd))
n = with(avg_exp,tapply(rating_count[author_sex=='female'], author_exp[author_sex=='female'], length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = 2*(pnorm(z))
round_p = round(p,4)
data.frame(z,p,round_p)
```
**Results: The z-score = -2.583666	and p-value = 0.0098**
We have sufficient evidence to reject the null hypothesis.
The average rating count for experienced female authors is not equal to the average rating count of avg work count female authors.

ANOVA Test:

```{r}
summary(aov(master_data$rating_count[master_data$author_sex=='female']~as.factor(master_data$author_exp[master_data$author_sex=='female'])))
```

Pairwise T-test with unequal variances:
```{r}
p12 = t.test(master_data$rating_count[master_data$author_exp=='newbie' & master_data$author_sex=='female'], master_data$rating_count[master_data$author_exp=='average' & master_data$author_sex=='female'],var.equal = F)
p12
p13 = t.test(master_data$rating_count[master_data$author_exp=='newbie' & master_data$author_sex=='female'], master_data$rating_count[master_data$author_exp=='experienced' & master_data$author_sex=='female'],var.equal = F)
p13
p23 = t.test(master_data$rating_count[master_data$author_exp=='average' & master_data$author_sex=='female'], master_data$rating_count[master_data$author_exp=='experienced' & master_data$author_sex=='female'],var.equal = F)
p23
```
