---
title: "Hypothesis 2"
author: "Anuhya B S"
date: "2/27/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**2. Authors can be classified based on years of experience or number of books published. Highly experienced authors can definitely be expected to have larger rating counts. From a publisher point of view, it would be useful to assess if publishing works of new authors (who typically have 0-3 works published) would look promising.**

$$H_0:\mu_N=\mu_A$$
__Test: Independent 2-tailed Z-test to compare mean rating count b/w New-comers and Average authors.__

```{r}
hypo2 = read.csv('./04 Intermediate Files/hypothesis2.csv')
```

```{r}
colnames(hypo2)
```
```{r}
hypo2 <- subset(hypo2, bins == 'newbie' | bins == 'experienced')
hypo2
```


```{r}
m = with(hypo2,tapply(rating_count, bins, mean))
s = with(hypo2,tapply(rating_count, bins, sd))
n = with(hypo2,tapply(rating_count, bins, length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = round(2*(pnorm(z)),4) 
data.frame(z,p)


```

**Grouping Hypothesis 1 & 2: It can also make sense to view the effect of author gender with author’s work exp (clubbing Hypothesis 1 & 2) on average rating count. We are not sure how it will play; so if there is insight - we would want to share.**

Comparing average rating counts of male newbies and female newbies
```{r}
m = with(hypo2,tapply(rating_count[bins=='newbie'], author_sex[bins=='newbie'], mean))
s = with(hypo2,tapply(rating_count[bins=='newbie'], author_sex[bins=='newbie'], sd))
n = with(hypo2,tapply(rating_count[bins=='newbie'], author_sex[bins=='newbie'], length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = round((pnorm(z)),4) 
data.frame(z,p)
```
We do not have enough evidence to reject the null hypothesis.
The average rating count for newbie female is equal to the average rating count of newbie male


Comparing average rating counts of male experienced and female experienced
```{r}
m = with(hypo2,tapply(rating_count[bins=='experienced'], author_sex[bins=='experienced'], mean))
s = with(hypo2,tapply(rating_count[bins=='experienced'], author_sex[bins=='experienced'], sd))
n = with(hypo2,tapply(rating_count[bins=='experienced'], author_sex[bins=='experienced'], length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = round(2*(pnorm(z)),4) 
data.frame(z,p)
```
We do not have enough evidence to reject the null hypothesis.
The average rating count for experienced male is equal to the average rating count of experienced female



Comparing average rating counts of male newbie and male experienced
```{r}
m = with(hypo2,tapply(rating_count[author_sex=='male'], bins[author_sex=='male'], mean))
s = with(hypo2,tapply(rating_count[author_sex=='male'], bins[author_sex=='male'], sd))
n = with(hypo2,tapply(rating_count[author_sex=='male'], bins[author_sex=='male'], length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = round((pnorm(z)),4) 
data.frame(z,p)
```

We do not have enough evidence to reject the null hypothesis.
The average rating count for newbie male is equal to the average rating count of experienced male.


Comparing average rating counts of female newbie and female experienced
```{r}
m = with(hypo2,tapply(rating_count[author_sex=='female'], bins[author_sex=='female'], mean))
s = with(hypo2,tapply(rating_count[author_sex=='female'], bins[author_sex=='female'], sd))
n = with(hypo2,tapply(rating_count[author_sex=='female'], bins[author_sex=='female'], length))
data.frame(m,s,n)
z = (m[1]-m[2])/sqrt(sum(s^2/n))
p = round(2*(pnorm(z)),4) 
data.frame(z,p)
```

We do not have enough evidence to reject the null hypothesis.
The average rating count for newbie female is equal to the average rating count of experienced female.